---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `msst2ap`

<!-- badges: start -->

<!-- badges: end -->

The goal of `msst2ap` (**M**astering **s**hiny **s**hiny**t**est**2** **a**pp-**p**ackage) is to demonstrate how to test a shiny app-package using [`testthat`](https://testthat.r-lib.org/) and [`shinytest2`](https://rstudio.github.io/shinytest2/)

## Installation

You can install `msst2ap` from GitHub using the code below: 

```{r}
#| eval: false
#| echo: true
remotes::install_github("mjfrigaard/msst2ap",
  force = TRUE, quiet = TRUE
)
```

```{r}
#| eval: true
#| echo: true
library(msst2ap)
```

## Set up 

There are specific instructions for setting up `shinytest2` in the [`shinytest2-setup.Rmd` vignette](https://github.com/mjfrigaard/msst2ap/blob/main/vignettes/shinytest2-setup.Rmd). 

## Utility function tests

The `find_vars()` function comes from [Mastering Shiny](https://mastering-shiny.org/scaling-modules.html#server-inputs), and it's used for filtering variables from a `data.frame`/`tibble` by type: 

```{r}
#| eval: true
#| echo: true
find_vars(data = airquality, filter = is.numeric)
```

View the unit tests in the [`unit-tests.Rmd` vignette](https://github.com/mjfrigaard/msst2ap/blob/main/vignettes/unit-tests.Rmd)


## `testServer()` tests

Tests for the module server functions and standalone app functions are in the [`testserver-test.Rmd` vignette](https://github.com/mjfrigaard/msst2ap/blob/main/vignettes/testserver-tests.Rmd). 

All examples come from the [Modules chapter of Mastering Shiny.](https://mastering-shiny.org/scaling-modules.html) 
