---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `msst2ap`

<!-- badges: start -->

<!-- badges: end -->

The goal of `msst2ap` (Mastering shiny `shinytest2` app-package) is to demonstrate how to test a shiny application package using [`testthat`](https://testthat.r-lib.org/) and [`shinytest2`](https://rstudio.github.io/shinytest2/)

## Installation

You don't *have* to install the `msst2ap` package, but you might want to download it as an example (or read through [this post](https://mjfrigaard.github.io/posts/test-shiny-p4/) to learn about it's contents).

```{r}
library(msst2ap)
```


## Utility function tests

There is a single utility function in `msst2ap`: `find_vars()`

```{r}
#| eval: true
#| echo: false
fs::dir_tree("tests/testthat/", regexp = "find")
```

```{r}
#| eval: false
testthat::test_file("tests/testthat/test-find_vars.R")
```

```{verbatim}
#> [ FAIL 0 | WARN 0 | SKIP 0 | PASS 4 ]
```


## `testServer()` tests

The unit tests using `shiny`'s `testServer()` function are below. 

### Module server function tests

These modules come from the [Modules chapter of Mastering Shiny.](https://mastering-shiny.org/scaling-modules.html) 

```{r}
#| eval: true
#| echo: false
fs::dir_tree("tests/testthat/", regexp = "Server")
```

```{r}
#| eval: false
#| echo: false
test_file("tests/testthat/test-datasetServer.R")
```

````{verbatim}
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 1 ]
	   datasetServer: dataset$input is NULL 
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 2 ]
	   datasetServer: dataset$input 
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 3 ]
	   datasetServer: class(session$returned()) 
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 4 ]
	   datasetServer: is.matrix(session$returned()) 
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 5 ]
	   datasetServer: typeof(session$returned()) 
```

```{r}
#| eval: false
#| echo: false
test_file("tests/testthat/test-selectVarServer.R")
```

````{verbatim}
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 1 ]
	   selectVarServer: is.reactive(data()) 
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 2 ]
	   selectVarServer: find_vars() 
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 3 ]
	   selectVarServer: input$var 
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 4 ]
	   selectVarServer: session$returned()
```

```{r}
#| eval: false
#| echo: false
test_file("tests/testthat/test-selectDataVarServer.R")
```

````{verbatim}
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 1 ]
	   selectDataVarServer: is.reactive(data) 
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 2 ]
	   selectDataVarServer: is.reactive(var) 
```


### Standalone app function tests

These apps come from the [Modules chapter of Mastering Shiny.](https://mastering-shiny.org/scaling-modules.html) 

```{r}
#| eval: true
#| echo: false
fs::dir_tree("tests/testthat/", regexp = "App")
```


```{r}
#| eval: false
#| echo: false
test_file("tests/testthat/test-datasetApp.R")
```

````{verbatim}
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 1 ]
	   datasetApp: input$`dataset-dataset` 
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 2 ]
	   datasetApp: is.data.frame(data()) 
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 3 ]
	   datasetApp: names(data()) 
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 4 ]
	   datasetApp: class(output$data) 
```

```{r}
#| eval: false
#| echo: false
test_file("tests/testthat/test-selectVarApp.R")
```

````{verbatim}
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 1 ]
	   selectVarApp: is.reactive(var) 
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 2 ]
	   selectVarApp: input$`var-var` 
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 3 ]
	   selectVarApp: is.reactive(data) 
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 4 ]
	   selectVarApp: is.data.frame(data()) 
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 5 ]
	   selectVarApp: data()[[input$`var-var`]] 
```

```{r}
#| eval: false
#| echo: false
test_file("tests/testthat/test-selectDataVarApp.R")
```

````{verbatim}
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 1 ]
	   selectDataVarApp: input$`var-var-var` 
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 2 ]
	   selectDataVarApp: input$`var-data-dataset` 
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 3 ]
	   selectDataVarApp: is.reactive(var) 
```

```{verbatim}
🐝 Your tests are the bee's knees 🐝
```
