---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `msst2ap`

<!-- badges: start -->

<!-- badges: end -->

The goal of `msst2ap` (**M**astering **s**hiny **s**hiny**t**est**2** **a**pp-**p**ackage) is to demonstrate how to test a shiny app-package using [`testthat`](https://testthat.r-lib.org/) and [`shinytest2`](https://rstudio.github.io/shinytest2/)

## Installation

You don't *have* to install the `msst2ap` package, but you might want to download it as an example (or read through [this post](https://mjfrigaard.github.io/posts/test-shiny-p4/) to learn about it's contents).

```{r}
library(msst2ap)
```


## Utility function tests

The `find_vars()` function comes from [Mastering Shiny](https://mastering-shiny.org/scaling-modules.html#server-inputs), and it's used for filtering variables from a `data.frame`/`tibble` by type: 

```{r}
#| eval: true
#| echo: true
find_vars(data = airquality, filter = is.numeric)
```


```{r}
#| eval: true
#| echo: false
fs::dir_tree("tests/testthat/", regexp = "utils")
```

```{r}
#| eval: false
testthat::test_file("tests/testthat/test-utils_find_vars.R")
```

```{verbatim}
#> [ FAIL 0 | WARN 0 | SKIP 0 | PASS 4 ]
```

## Package datasets

I've added some additional unit tests for the utility functions in the `ggHistogramApp()`

## `pkg_inst_check()`

`pkg_inst_check` will check if a package is installed, and if not, install it.

```{r}
#| eval: true 
#| echo: true
if ("emoji" %in% loadedNamespaces()) {
  # remove from ns
  remove.packages("emoji")
} else {
  # with single pkg
  pkg_inst_check("emoji")
}
```

```{r}
#| eval: true 
#| echo: true
if (any(c("palmerpenguins", "snakecase") %nin% loadedNamespaces())) {
    # with multiple pkgs
    pkgs <- c("palmerpenguins", "snakecase")
    pkg_inst_check(pkgs)
}
```

## `find_pkg_df_nms()`

The `find_pkg_df_nms()` function will return a named vector of `data.frame`s/`tibble`s in a package.

It works with base packages: 

```{r}
#| eval: true 
#| echo: true 
#| message: false 
#| warning: false
pkg_inst_check("forcats")
find_pkg_df_nms(pkg = "forcats")
```

And add-on packages:

```{r}
#| eval: true 
#| echo: true 
#| message: false 
#| warning: false
find_pkg_df_nms(pkg = "datasets")
```

If there are no `data.frame`s/`tibble`s, it returns nothing.

```{r}
#| eval: true 
#| echo: true 
#| message: false 
#| warning: false
find_pkg_df_nms(pkg = "utils")
find_pkg_df_nms(pkg = "stats")
```

## `pkg_df_check()` 

`pkg_df_check()` is a helper function that returns a `TRUE`/`FALSE` if the package contains at least one `data.frame`/`tibble`: 

```{r}
#| eval: true 
#| echo: true 
#| message: false 
#| warning: false
pkg_df_check("datasets")
pkg_df_check("stringr")
```

## `find_df_pkgs()` 

`find_df_pkgs()` is the real workhorse of the `msst2ap` package--it returns the installed packages with `data.frame`s/`tibble`s: 

```{r}
#| eval: true 
#| echo: true 
#| message: false 
#| warning: false
find_df_pkgs()
```

## `get_pkg_df()` 

`get_pkg_df()` is similar to `get()`, but has a slightly more intuitive API (i.e., only needs the `pkg` and `df`)

```{r}
#| eval: true 
#| echo: true 
#| message: false 
#| warning: false
get_pkg_df(df = "starwars", pkg = "dplyr")
```



## `testServer()` tests

The unit tests using `shiny`'s `testServer()` function are below. 

### Module server function tests

These modules come from the [Modules chapter of Mastering Shiny.](https://mastering-shiny.org/scaling-modules.html) 

```{r}
#| eval: true
#| echo: false
fs::dir_tree("tests/testthat/", regexp = "Server")
```

```{r}
#| eval: false
#| echo: false
test_file("tests/testthat/test-datasetServer.R")
```

```{verbatim}
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 1 ]
	   datasetServer: dataset$input is NULL 
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 2 ]
	   datasetServer: dataset$input 
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 3 ]
	   datasetServer: class(session$returned()) 
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 4 ]
	   datasetServer: is.matrix(session$returned()) 
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 5 ]
	   datasetServer: typeof(session$returned()) 
```

```{r}
#| eval: false
#| echo: false
test_file("tests/testthat/test-selectVarServer.R")
```

```{verbatim}
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 1 ]
	   selectVarServer: is.reactive(data()) 
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 2 ]
	   selectVarServer: find_vars() 
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 3 ]
	   selectVarServer: input$var 
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 4 ]
	   selectVarServer: session$returned()
```

```{r}
#| eval: false
#| echo: false
test_file("tests/testthat/test-selectDataVarServer.R")
```

```{verbatim}
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 1 ]
	   selectDataVarServer: is.reactive(data) 
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 2 ]
	   selectDataVarServer: is.reactive(var) 
```


### Standalone app function tests

These apps come from the [Modules chapter of Mastering Shiny.](https://mastering-shiny.org/scaling-modules.html) 

```{r}
#| eval: true
#| echo: false
fs::dir_tree("tests/testthat/", regexp = "App")
```


```{r}
#| eval: false
#| echo: false
test_file("tests/testthat/test-datasetApp.R")
```

```{verbatim}
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 1 ]
	   datasetApp: input$`dataset-dataset` 
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 2 ]
	   datasetApp: is.data.frame(data()) 
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 3 ]
	   datasetApp: names(data()) 
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 4 ]
	   datasetApp: class(output$data) 
```

```{r}
#| eval: false
#| echo: false
test_file("tests/testthat/test-selectVarApp.R")
```

```{verbatim}
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 1 ]
	   selectVarApp: is.reactive(var) 
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 2 ]
	   selectVarApp: input$`var-var` 
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 3 ]
	   selectVarApp: is.reactive(data) 
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 4 ]
	   selectVarApp: is.data.frame(data()) 
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 5 ]
	   selectVarApp: data()[[input$`var-var`]] 
```

```{r}
#| eval: false
#| echo: false
test_file("tests/testthat/test-selectDataVarApp.R")
```

```{verbatim}
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 1 ]
	   selectDataVarApp: input$`var-var-var` 
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 2 ]
	   selectDataVarApp: input$`var-data-dataset` 
[ FAIL 0 | WARN 0 | SKIP 0 | PASS 3 ]
	   selectDataVarApp: is.reactive(var) 
```

```{verbatim}
ðŸ Your tests are the bee's knees ðŸ
```
